Does pre-crastination explain why some observers are sub-optimal in a visual search task?

### 2023-09-06 RegReport/paper.tex
Update paper.tex

Data from participants who fail to achieve at least $75\%$ accuracy for \textit{easy} and \textit{absent} conditions will be excluded as it suggests that they did not understand the task. Fixations during trials will be classified as falling on the homogeneous or heterogeneous half of the display, with fixations falling within the central four columns of line segments being excluded. Following \cite{nowakowska2017} we will summarise each participant's strategy as the proportion of fixations two through five falling on the heterogeneous side of the display during target absent trials. Trials with fewer than five fixations will be excluded, and we will only analysis data from participants who have at least 10 trials.

@@

PPersonality questionnaires will be administered to participants at the end of the experiment to prevent them from influencing the behavioural measures. Questionnaires will be hosted on Qualtrics and participants will access the questionnaires using a laboratory computer.

@@

The first step of our planned analysis is to test the hypothesis that there is a difference in  visual search strategy between those participants who pre-crastinated and those who did not. As registered, we fit a Bayesian beta regression model, the results of which are displayed in Figure \ref{fig:full_exp_strategy}. There is little-to-no evidence for a difference between the two groups, ($p(\delta >0| X)  =0.50$). This lack of differences makes hypothesis ii (that the effect size will be in line with the pilot data) redundant, but we report the $95\%$ HPDI $= [-0.0465, 0.0467$] for completeness sake.

@@

\subsubsection{Personality and Pre-crastination}
The left column of Figure \ref{fig:exp_analysis} shows the relationship between 10 personality measures and precrastination in a sample of 304 participants. The width of the bar is the range of the $95\%$ CI around the difference between precrastinators and non-precastinators on each measure. Most measures are close to 0 (the vertical dashed line). We find some tentative evidence to suggest that participants who pre-crastinate may score slightly higher in impulsivity and lower in extraversion and open-mindedness. We did not make any specific predictions about these personality measures, and so we refrain from interpreting these, but report them here for the benefit of future research (with the caution that if the effect size estimates based on a sample of such a large size are close to 0, they will be diffiult to detect).

@@

The relationship between conscientiousness and pre-crastination observed previously \cite{sauerberger2019} was not observed here. This could be because the original effect was a statistical accident, or because the effect is small and not present in our sample. One point to note is that our sample was skewed towards the higher end of the conscientiousness scale, likely because unconscientious people are less inclined to participate in psychology experiments. It is possible that the sample in \cite{sauerberger2019} was more representative of the full range of conscientiousness in the population, and was therefore more sensitive to the relationship with precrastination. On the other hand, one might expect our more conscientious sample would have higher precrastination rates than previously observed, and this was not the case. Another interesting and counterintuitive observation from \cite{sauerberger2019} was that procrastination was unrelated to precrastination, and the current results show a small negative correlation, as one would expect if starting tasks too soon is predictive of not starting tasks too late. Overall, we have a rich dataset here with many other measures and we invite others to use it in hypothesis-generating exploratory analyses of their choosing. We request that anyone using the data in this repository reference this paper.

>>>>

Data from participants who fail to achieve at least $75\%$ accuracy for \textit{easy} and \textit{absent} conditions will be excluded as it suggests that they did not understand the task. Fixations during trials will be classified as falling on the homogeneous or heterogeneous half of the display, with fixations falling within the central four columns of line segments being excluded. Following \cite{nowakowska2017} we will summarise each participant's strategy as the proportion of fixations two through five falling on the heterogeneous side of the display during target absent trials. Trials with fewer than five fixations will be excluded, and we will only analyse data from participants who have at least 10 trials.

@@

Personality questionnaires will be administered to participants at the end of the experiment to prevent them from influencing the behavioural measures. Questionnaires will be hosted on Qualtrics and participants will access the questionnaires using a laboratory computer.

@@

The first step of our planned analysis is to test the hypothesis that there is a difference in  visual search strategy between those participants who pre-crastinated and those who did not. As registered, we fit a Bayesian beta regression model, the results of which are displayed in Figure \ref{fig:full_exp_strategy}. There is little-to-no evidence for a difference between the two groups, ($p(\delta >0| X)  =0.50$). This lack of differences makes hypothesis ii (that the effect size will be in line with the pilot data) redundant, but we report the $95\%$ HPDI $= [-0.0465, 0.0467$] for the sake of completeness.

@@

\subsubsection{Personality and Pre-crastination}
The left column of Figure \ref{fig:exp_analysis} shows the relationship between 10 personality measures and precrastination in a sample of 304 participants. The width of the bar is the range of the $95\%$ CI around the difference between precrastinators and non-precastinators on each measure. We find some tentative evidence to suggest that participants who pre-crastinate may score slightly higher in impulsivity and lower in extraversion and open-mindedness. We did not make any specific predictions about these personality measures, and so we refrain from interpreting these, but report them here for the benefit of future research, with the caution that many of the effect size estimates cover a range that includes or is close to 0, even with this large sample.

@@

The relationship between conscientiousness and pre-crastination observed previously \cite{sauerberger2019} was not observed here. This could be because the original effect was a statistical accident, or because the effect is small and not present in our sample. One point to note is that our sample was skewed towards the higher end of the conscientiousness scale, likely because unconscientious people are less inclined to participate in psychology experiments. It is possible that the sample in \cite{sauerberger2019} was more representative of the full range of conscientiousness in the population, and was therefore more sensitive to the relationship with precrastination. On the other hand, one might expect our more conscientious sample would have higher precrastination rates than previously observed, and this was not the case. Another interesting and counterintuitive observation from \cite{sauerberger2019} was that procrastination was unrelated to precrastination, and the current results show a small negative correlation, as one would expect if starting tasks too soon is predictive of not starting tasks too late.

Our results provide a relatively definitive answer to a set of similar questions that have been posed with some frequency by other researchers in review comments and in discussions at conferences and research meetings: can we explain variation in individual strategies in these two tasks using these well-established questionnaires? Although the simple answer is "no", the hypothesis that personality traits can explain or predict behaviour in these tasks cannot be completely put to rest by our results, because it is possible the relationships are nonlinear, or there are heterogeneous influences that can drive two people to exhibit the same behaviour, but for different reasons. Nonetheless, had we found the predicted relationships in the larger sample, this would have been an important finding, that would have indicated we can predict how people behave in these tasks based on personality traits (and vice-versa). It was therefore an important possibility to test, even though the results did not bear out the prediction. Moreover, through this project, we have produced a large and very rich dataset with many other measures included, in addition to those reported here. We invite others to use it in hypothesis-generating exploratory analyses of their choosing. We request that anyone using the data in this repository reference this paper.
